### 2010-02-17 doc/manuals/janitor/tex_maintenance/maintenance.tex
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.

\section{Introducing new packages}\label{sec:catalog}\label{sec:introducing_new_packages}

@@

The WEKA package for machine learning~\cite{FRANK_20074} and the Java
Runtime Environment are available as dynamic Runtime Environments. Further
packages for bioinformatics comprise dynamic variants of tools for
the analysis of transcription factor binding sites. These are already
offered for manual installation via the prior mentioned traditional page
representing Runtime Environments for ARC.
The \texttt{data} directory simply contains
a ZIP file which needs to be unzipped in the installation directory. For
that reason, the \texttt{control/install} script is written as follows:

>>>>

\section{Introducing new packages}\label{sec:introducing_new_packages}

@@

The WEKA package for machine learning~\cite{FRANK_2004} and the Java
Runtime Environment are available as dynamic Runtime Environments. Further
packages for bioinformatics comprise dynamic variants of tools for
the analysis of transcription factor binding sites. These are already
offered for manual installation via the prior mentioned traditional page
representing Runtime Environments for ARC.
The \texttt{data} directory simply contains
a ZIP file which needs to be unzipped in the installation directory. For
that reason, the \texttt{control/install} script is written as follows:
